Universal Anonymous Signatures

### 2022-10-03 prism-backend/research/gsac/formal-uas.tex
Pass.

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all other functions.
\item[$\KeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, a user runs
  \KeyGen to generate its user key pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\ISet(\upk,\usk,\fissue) \rightarrow \ipk$.] Given a user key
  pair, and an issuance function \fissue for checking that credential requestors
  meet some conditions to be issued a credential, an existing user runs \ISet to
  extend the user public key, enabling this user to issue credentials meeting
  \fissue.
%\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
%  key pair.
\item[$\langle
  \Obtain(\usk,\ipk,\sCred,\attrs),
  \Issue(\isk,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,R/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk receive a credential
  $\Cred=(\cid,\attrs,\cred,\ipk)$
  from an issuer in the system. $\cid=(\cidi,\cidu)$ is a unique identifier for
  the credential, where issuer and user randomly pick \cidi and \cidu,
  respectively (to ease notation, whenever we write just \cid, we mean $(\cidi,
  \cidu)$). \ipk is the issuer's public key and \cred is the actual credential,
  on attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i=(\cidi_i,\cidu_i),\cattrs_i,\cred_i,
  \ipk_i)\rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for
  readability. The user outputs the produced credential \Cred, while the issuer
  outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
  the \fissue function defined by the issuer, and $\utrans=(U,I)$ being the
  transcript of the communication, where $U$ contains the messages sent by
  the user, and $I$ those sent by the issuer.
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving user secret key \usk, opener public key \opk, 
  credentials \sCred, message \msg and evaluation function \feval, returns
  signature \sig, and a value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Run by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials by issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

\paragraph{Issuance, evaluation, and opening functions.} %
These are the functional placeholders that allow modulating the behaviour of the
resulting instantiation, by controling the conditions upon which new credentials
can be issued, the information revealed at signing time, or extractable from
signatures. In all cases, the user who computes them, and proves correctness of
such computation. We give concrete examples in \secref{sec:relationships}.

@@

\feval and \finsp may seem redundant. However, the former is chosen on a
per-signature basis, probably after negotiation between signer and verifier, and
governs the information revealed at signing time. On the other hand, \finsp
governs the information that may be revealed after signing, and is defined by
openers when they set up their key pair.

Concerning \fissue functions, our \UAS model requires them to be
\UAS-acceptable. At a high level, this requires that \fissue functions do not
reveal anything about the signer's data used as input. This is formally captured
in \figref{fig:uas-acceptable}.
%
A \UAS construction thus can only be secure if the \fissue functions it uses
are \UAS-acceptable.

\begin{figure}[ht!]
  \centering  
  \scalebox{0.85}{
    \procedure{$\Exp^{\UAS-acc-b}_\adv(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\upk,\usk) \gets \KeyGen(\parm) \\
      (\st,\attrs, \lbrace (\cidi,\cidu,\cattrs_i) \rbrace_{i\in[n]})
      \gets \adv(\upk) \\
      \pcif b=0:
      \yissue^* \gets \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\cattrs_i)
      \rbrace_{i\in[n]}) \\
      \pcelse: \yissue^* \getr \rngfissue \setminus \lbrace 0 \rbrace \\
      b^* \gets \adv(\st,\yissue^*) \\
      \pcreturn b^*
    }
  }
  \label{fig:uas-acceptable}
  \caption{Formal definition of \UAS-acceptable \fissue functions.}
\end{figure}

@@

\paragraph{Global Variables.} %
Users are referred to with user identifiers, \uid; for credentials, we use \cid;
and for openers, \oid. Although issuers are ``extended'' users, and thus can be
identified by their \uid, we mostly use \iid to refer to a user acting as
issuer, especially, for operations involving both a user and an issuer.
%
For notational convenience, we often use these identifiers instead of the
corresponding user/issuer/opener keys.
%
All tables/sets are initialized as empty tables/sets. We use the following sets
and tables in our definitions:

@@

\paragraph{Unforgeability.} In \UAS schemes, we need to prevent forging either
credential requests, and signatures. The latter is mostly a combination of the
unforgeability of AC schemes, and the traceability of GS schemes with verifiable
openings. However, the need for issuance unforgeability is a consequence of
allowing to support credential requests with previously obtained credentials --
functionality which, to the best of our knowledge, \UAS is the first scheme
to support. In both cases, it is necessary to assume honest issuers.

Signature unforgeability, \ExpForgeSign, is mainly a combination (and
generalisation) of known requirements in AC and GS schemes. Namely, the
adversary is required to output a valid signature, from which we extract the
user key pair, credentials, $\yeval^1$ and \yinsp values used to generate the
signature. The adversary wins if the signature: (1) opens to a wrong value, or
to a value that cannot be processed by \Judge; (2), is not consistent with the
expected $\Yeval = (\yeval^0,\yeval^1)$ value; or (3), cannot be associated to
credentials owned by a known user. Here, we again need to assume honest issuers.
Otherwise, it is trivial for the adversary to produce untraceable credentials
(i.e., that do not appear in any ``log'') which then evaluate to any desired
value when used to generate a signature.

While it may seem enough to check that no valid signature can be created from
forged credentials (i.e., credentials that did not meet their issuance policy,
or are not bound to a known user), note that allowing credentials to
endorse further credential requests makes this argument insufficient. For
instance, if we only check the credentials involved in signature generation, it
is perfectly possible that a forged credential is used to obtain a legitimate
one, and then use the latter to finally create a valid signature -- concretly,
such misbehaviour is not prevented by \ExpForgeSign.

We thus extend unforgeability of signatures with issuance unforgeability,
\ExpForgeIssue. It captures that all honestly issued credentials meet the
requirements set by the corresponding issuer, and that any further credential
involved in the request is bound to the same known user. For this, we allow the
adversary \adv~to interact with the oracles (restricted to honest issuers).
Eventually, \adv~is challenged to output a credential identifier from which we
extract the actual witnesses used in the credential request associated to \cid.
\adv~wins if the issuance function, applied to the extracted values, does not
meet the expected output, or if not all of the credentials (if any) used to
support the request belong to a same (known) user. Note that the issuance
transcript associated to \cid must exist, as we unavoidably need to restrict to
honest issuers. Indeed, a dishonest issuer cannot be trusted to enforce any
policy, nor to properly keep all transcripts. In practice, this means that
dishonest issuers can create arbitrary credentials.

@@

\begin{figure}[htp!]
  \centering
  \hspace*{-2em}
  \scalebox{0.85}{
    \begin{minipage}[t]{0.6\textwidth}
      \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        % (\Cred,\uid,\iid,\oid,\feval,\msg) \gets \adv^{\Oforge}(\parm) \\
        % \Sig \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\Cred,\msg,\feval) \\
        % \pcif \Verify(\PUBOK[\oid],\PUBIK[\iid],\Sig,\msg,\feval) = 0: \\
        % \pcind \pcreturn 0 \\
        % (\upk,\usk, (\cid,\attrs,\cdot), \cdot, \cdot) \\
        % \pcind \gets \ExtractSign(\trap,\oid,\iid,\Sig,\msg,\feval) \\
        % \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 1 \\
        % (\yissue,\cdot) \gets \trans[\cid];
        % ((\cdot,\fissue),\cdot) \gets \PUBIK[\cid] \\
        % \pcif \nexists \lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]}
        % \in \CRED[\uid]~\suchthat \\
        % \pcind \fissue(\upk,\cid,\attrs,
        % \lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]}) = \yissue: \\
        % \pcind \pcreturn 1
        % 
        % ((\upk_1,r_1,\Ccom_1),\dots,(\upk_l,r_l,\Ccom_l),\st) \\
        % \pcind \gets \adv^{\HUGEN,\CUGEN}(\texttt{choose},\parm) \\
        % \pcif \exists i\in[l]~\suchthat~\forall \uid,
        % \upk_i \neq \PUBUK[\uid]:  \\
        % \pcind \pcreturn 0 \\
        % \cid \gets \adv^{\Oforge}(\texttt{forge},\st,\parm) \\
        \cid \gets \adv^{\Oforge}(\parm) \\
        \pcif \ISR[\cid] \notin \HI \lor \trans[\cid] = \bot: \pcreturn 0 \\
        (\utrans,\yissue) \gets \trans[\cid] \\
        (\upk,\cdot,\lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]},\cdot,\attrs,
        \cdot) \gets \ExtractIssue(\trap,\utrans) \\
        \textrm{Let $\scid \gets \lbrace \cid_i \rbrace_{i\in[n]} \cup
          \lbrace \cid \rbrace$} \\
        \pcreturn \OWNR[\scid] \notin \HU \cup \CU~\lor \\
        \pcind \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\attrs_i)\rbrace_{i\in[n]})
        \neq \yissue
      }      
    \end{minipage}    
    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering=on]{$\ExpForgeSign(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        (\oid,\siid,\Sig=(\sig,\tyeval^0),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
        \pcif \exists \iid \in \siid~\suchthat~\iid \notin \HI \lor
        \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
        \SIG[\uid]~\lor  \\
        \pcind \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0: \\
        \pcind \pcreturn 0 \\
        (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
	(\upk,\usk,\lbrace(\cid_i,\attrs_i,\cred_i)\rbrace_{i\in[n]},
        \tyeval^1,\tyinsp) % \pcskipln
        \\
        \pcind \gets \ExtractSign(\trap,\Sig) \\
        (\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]}, \msg) \\
        \pcreturn \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \notin
        \HU \cup \CU~\lor \\
        \pcind \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,
        \msg,\feval) = 0~\lor \\
        \pcind \yeval^0 \neq \tyeval^0 \lor \yeval^1 \neq \tyeval^1 \lor
        \yinsp \neq \tyinsp~\lor\\
        \pcind \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]},\msg) \neq \yinsp 
      }
    \end{minipage}
  }
  \caption{Unforgeability experiments in \UAS schemes.
    $\Oforge \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace
    \CORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$. % In line 10 of \ExpForgeIssue, we
    % slightly abuse notation to denote that user \uid does not own a set of
    % credentials with {\cid}s and attributes equal to $\lbrace (\cid_i,\attrs_i)
    % \rbrace_{i\in[n]}$.
  }
  \label{fig:exp-uas-unfor}
\end{figure}

@@

\begin{definition}{(Unforgeable signing of \UAS)}
  \label{def:sign-forge-uas}  
  We define the advantage \AdvForgeSign of $\adv$ against \ExpForgeSign as
  $\AdvForgeSign=\Pr\lbrack\ExpForgeSign(1^\secpar)=1\rbrack$.
  %
  A \UAS scheme has unforgeable signing if, for any p.p.t. adversary $\adv$,
  \AdvForgeSign is a negligible function of $1^\secpar$.
\end{definition}

@@

\paragraph{Non-frameability.} %
The notion of non-frameability in \UAS schemes is unavoidably more subtle than
in group signatures\footnote{As far as we know, non-frameability has not been
  considered in anonymous credential schemes. Thus, \UAS is the first scheme
  that concretely models what can we expect, unforgeability-wise, in the
  presence of malicious issuers in the AC domain.}. To see
this, note that, by allowing arbitrary evaluation and open functions to be used,
it can be perfectly valid to have a signature produced by a corrupted user
output the same \Yeval or \yinsp values than the ones output when evaluating or
opening a signature by an honest user.
%
More generally, since the issuer is dishonest in non-frameability properties
and, in \UAS, the value produced by \Open may depend on the attributes
included in user credentials, the adversary may even be able to just produce
``legitimate'' openings to any desired value. Anyway, this is
a relevant property, as it tells us the minimal unforgeability expectations we
can have, even against malicious issuers and openers.

In the non-frameability definition for \UAS, given in experiment \ExpNonframe in
\figref{fig:exp-uas-frame}, the adversary is challenged to produce a signature
and opening proof that is accepted by \Verify and \Judge, respectively. From
the signature, we then extract the secret data used to generate it. The
adversary wins if the signature and opening proof are accepted, but the \yeval
or \yinsp values do not match what they should be based on the extracted data;
or if the signature can be associated to the secret key of an honest user who
did not produce it (i.e., no matching call to \SIGN exists).

>>>>

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all other functions.
\item[$\KeyGen(\parm) \rightarrow (% \Ccom,r,
  \upk,\usk)$.] Given \parm, a user
  runs \KeyGen to generate its user key pair% , and a commitment \Ccom to the
  % public key, with randomness $r$
  . 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\ISet(\upk,\usk,\fissue) \rightarrow \ipk$.] Given a user key
  pair, and an issuance function \fissue for checking that credential requestors
  meet some conditions to be issued a credential, an existing user runs \ISet to
  extend the user public key, enabling this user to issue credentials meeting
  \fissue.
%\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
%  key pair.
\item[$\langle
  \Obtain(\usk,\ipk,\sCred,\attrs),
  \Issue(\isk,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,R/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk receive a credential
  $\Cred=(\cid,\attrs,\cred,\ipk)$
  from an issuer in the system. $\cid=(\cidi,\cidu)$ is a unique identifier for
  the credential, where issuer and user randomly pick \cidi and \cidu,
  respectively (to ease notation, whenever we write just \cid, we mean $(\cidi,
  \cidu)$). \ipk is the issuer's public key and \cred is the actual credential,
  on attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i=(\cidi_i,\cidu_i),\cattrs_i,\cred_i,
  \ipk_i)\rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for
  readability. The user outputs the produced credential \Cred, while the issuer
  outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
  the \fissue function defined by the issuer, and $\utrans=(U,I)$ being the
  transcript of the communication% , where $U$ contains the messages sent by
  % the user, and $I$ those sent by the issuer
  .
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving user secret key \usk, opener public key \opk, 
  credentials \sCred, message \msg and evaluation function \feval, returns
  signature \sig, and a value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Run by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials by issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

\paragraph{Issuance, evaluation, and opening functions.} %
These are the functional placeholders that allow modulating the behaviour of the
resulting instantiation. They controll the conditions upon which new credentials
can be issued, the information revealed at signing time, or extractable from
signatures. In all cases, the user computes them, and proves correctness of
such computation. We give concrete examples in \secref{sec:relationships}.

@@

Concerning \fissue functions, our \UAS model requires them to be
\UAS-acceptable. At a high level, this requires that, conditioned on \fissue
functions accepting the request (i.e., returning a non-zero value), they do not
reveal anything about the signer's data used as input. This is formally captured
in \figref{fig:uas-acceptable}.
%
A \UAS construction thus can only be secure if the \fissue functions it uses
are \UAS-acceptable.

\begin{figure}[ht!]
  \centering  
  \scalebox{0.85}{
    \procedure[linenumbering=on]{$\Exp^{\UAS-acc-b}_\adv(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\upk,\usk) \gets \KeyGen(\parm) \\
      (\st,\attrs, \lbrace (\cidi,\cidu,\cattrs_i) \rbrace_{i\in[n]})
      \gets \adv(\upk) \\
      y \gets \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\cattrs_i)
      \rbrace_{i\in[n]}) \\
      \pcif y = 0: \pcreturn \bot \\
      \pcif b=0: \yissue^* \gets y;~
      \pcelse:~\yissue^* \getr \rngfissue \setminus \lbrace 0 \rbrace \\
      b^* \gets \adv(\st,\yissue^*) \\
      \pcreturn b^*
    }
  }
  \label{fig:uas-acceptable}
  \caption{Formal definition of \UAS-acceptable \fissue functions.}
\end{figure}

@@

\paragraph{Global Variables.} %
Users are referred to with user identifiers, \uid; for credentials, we use \cid;
and for openers, \oid. Although issuers are ``extended'' users, and thus can be
identified by their \uid, we mostly use \iid to refer to a user acting as
issuer, especially for clarity in operations involving both a user and an
issuer.
%
For notational convenience, we often use these identifiers instead of the
corresponding user/issuer/opener keys.
%
All tables/sets are initialized as empty tables/sets. We use the following sets
and tables in our definitions:

@@

\paragraph{Unforgeability.} In \UAS schemes, we need to prevent forging either
credential requests, and signatures. The latter is mostly a combination of the
unforgeability of AC schemes, and the traceability of GS schemes with verifiable
openings. However, the need for issuance unforgeability is a consequence of
allowing users to leverage previously obtained credentials in new credential
requests -- functionality which, to the best of our knowledge, \UAS is the first
scheme to support. In both cases, it is necessary to assume honest issuers.

Signature unforgeability, \ExpForgeSign, is mainly a combination (and
generalisation) of known requirements in AC and GS schemes. Namely, the
adversary is required to output a valid signature, from which we extract the
user key pair, credentials, $\yeval^1$ and \yinsp values used to generate the
signature. The adversary wins if the signature: (1) opens to a wrong value, or
to a value that cannot be processed by \Judge; (2), is not consistent with the
expected $\Yeval = (\yeval^0,\yeval^1)$ value; or (3), cannot be associated to
credentials owned by a known user. Here, we need to assume honest issuers.
Otherwise, it is trivial for the adversary to produce untraceable credentials
(i.e., that do not appear in any ``log'') which then evaluate to any desired
value when used to generate a signature.

We could simply check that all the credetnials involved in valid signatures
satisfy their respective \fissue functions, and belong to known users. However,
allowing credentials to endorse further credential requests makes this argument
insufficient. For instance, if we only check the credentials involved in
signature generation, it is perfectly possible that a forged credential is used
to obtain a legitimate one, and then use the latter to finally create a valid
signature -- concretly, such misbehaviour is not prevented by \ExpForgeSign.

We thus extend unforgeability of signatures with issuance unforgeability,
\ExpForgeIssue. It captures that all honestly issued credentials meet the
requirements set by the corresponding issuer, and that any further credential
involved in the request is bound to the same known user. For this, we allow the
adversary \adv~to interact with the oracles (restricted to honest issuers).
Eventually, \adv~is challenged to output a credential identifier from which we
extract the actual witnesses used in the credential request associated to \cid.
\adv~wins if the issuance function, applied to the extracted values, does not
meet the expected output, or if not all of the credentials (if any) used to
support the request belong to the same (known) user to whom the new credential
was issued. Note that the issuance transcript associated to \cid must exist, as
we unavoidably need to restrict to honest issuers. Indeed, a dishonest issuer
cannot be trusted to enforce any policy, nor to properly keep all transcripts.

@@

\begin{figure}[htp!]
  \centering
  \hspace*{-2em}
  \scalebox{0.85}{
    \begin{minipage}[t]{0.6\textwidth}
      \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        % (\Cred,\uid,\iid,\oid,\feval,\msg) \gets \adv^{\Oforge}(\parm) \\
        % \Sig \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\Cred,\msg,\feval) \\
        % \pcif \Verify(\PUBOK[\oid],\PUBIK[\iid],\Sig,\msg,\feval) = 0: \\
        % \pcind \pcreturn 0 \\
        % (\upk,\usk, (\cid,\attrs,\cdot), \cdot, \cdot) \\
        % \pcind \gets \ExtractSign(\trap,\oid,\iid,\Sig,\msg,\feval) \\
        % \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 1 \\
        % (\yissue,\cdot) \gets \trans[\cid];
        % ((\cdot,\fissue),\cdot) \gets \PUBIK[\cid] \\
        % \pcif \nexists \lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]}
        % \in \CRED[\uid]~\suchthat \\
        % \pcind \fissue(\upk,\cid,\attrs,
        % \lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]}) = \yissue: \\
        % \pcind \pcreturn 1
        % 
        % ((\upk_1,r_1,\Ccom_1),\dots,(\upk_l,r_l,\Ccom_l),\st) \\
        % \pcind \gets \adv^{\HUGEN,\CUGEN}(\texttt{choose},\parm) \\
        % \pcif \exists i\in[l]~\suchthat~\forall \uid,
        % \upk_i \neq \PUBUK[\uid]:  \\
        % \pcind \pcreturn 0 \\
        % \cid \gets \adv^{\Oforge}(\texttt{forge},\st,\parm) \\
        \cid \gets \adv^{\Oforge}(\parm) \\
        \pcif \ISR[\cid] \notin \HI \lor \trans[\cid] = \bot: \pcreturn 0 \\
        (\utrans,\yissue) \gets \trans[\cid] \\
        (\upk,\cdot,\lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]},\cdot,\attrs,
        \cdot) \gets \ExtractIssue(\trap,\utrans) \\
        \textrm{Let $\scid \gets \lbrace \cid_i \rbrace_{i\in[n]} \cup
          \lbrace \cid \rbrace$} \\
        \pcreturn \OWNR[\scid] \notin \HU \cup \CU~\lor \\
        \pcind \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\attrs_i)\rbrace_{i\in[n]})
        \neq \yissue
      }      
    \end{minipage}    
    \begin{minipage}[t]{0.6\textwidth}
      \procedure[linenumbering=on]{$\ExpForgeSign(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        (\oid,\siid,\Sig=(\sig,\tyeval^0),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
        \pcif \exists \iid \in \siid~\suchthat~\iid \notin \HI~\lor \\
        \pcind \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
        \SIG[\uid]~\lor  \\
        \pcind \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0: \\
        \pcind \pcreturn 0 \\
        (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
	(\upk,\usk,\lbrace(\cid_i,\attrs_i,\cred_i)\rbrace_{i\in[n]},
        \tyeval^1,\tyinsp) % \pcskipln
        \\
        \pcind \gets \ExtractSign(\trap,\Sig) \\
        (\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]}, \msg) \\
        \pcreturn \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \notin
        \HU \cup \CU~\lor \\
        \pcind \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,
        \msg,\feval) = 0~\lor \\
        \pcind \yeval^0 \neq \tyeval^0 \lor \yeval^1 \neq \tyeval^1 \lor
        \yinsp \neq \tyinsp~\lor\\
        \pcind \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]},\msg) \neq \yinsp 
      }
    \end{minipage}
  }
  \caption{Unforgeability experiments in \UAS schemes.
    $\Oforge \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace
    \CORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$. % In line 10 of \ExpForgeIssue, we
    % slightly abuse notation to denote that user \uid does not own a set of
    % credentials with {\cid}s and attributes equal to $\lbrace (\cid_i,\attrs_i)
    % \rbrace_{i\in[n]}$.
  }
  \label{fig:exp-uas-unfor}
\end{figure}

@@

\begin{definition}{(Unforgeable signatures of \UAS)}
  \label{def:sign-forge-uas}  
  We define the advantage \AdvForgeSign of $\adv$ against \ExpForgeSign as
  $\AdvForgeSign=\Pr\lbrack\ExpForgeSign(1^\secpar)=1\rbrack$.
  %
  A \UAS scheme has unforgeable signing if, for any p.p.t. adversary $\adv$,
  \AdvForgeSign is a negligible function of $1^\secpar$.
\end{definition}

@@

\paragraph{Non-frameability.} %
The notion in \UAS schemes is unavoidably more subtle than
in group signatures\footnote{As far as we know, non-frameability has not been
  considered in anonymous credential schemes. Thus, \UAS is the first scheme
  that concretely models what can we expect, unforgeability-wise, in the
  presence of malicious issuers in the AC domain.}. To see
this, note that, by allowing arbitrary evaluation and open functions to be used,
it can be perfectly valid to have a signature produced by a corrupted user
output the same \Yeval or \yinsp values than those output when evaluating or
opening a signature by an honest user.
%
More generally, since the issuer is dishonest in non-frameability properties
and, in \UAS, the value produced by \Open may depend on the attributes
included in user credentials, the adversary may even be able to produce
``legitimate'' openings to any desired value. Anyway, this is
a relevant property, as it tells us the minimal unforgeability expectations we
can have, even against malicious issuers and openers.

We formalize non-frameability in \ExpNonframe in \figref{fig:exp-uas-frame}.
The adversary is challenged to produce a signature
and opening proof that is accepted by \Verify and \Judge, respectively. From
the signature, we then extract the secret data used to generate it. The
adversary wins if the signature and opening proof are accepted, but the \yeval
or \yinsp values do not match what they should be based on the extracted data;
or if the signature can be associated to the secret key of an honest user who
did not produce it (i.e., no matching call to \SIGN exists).

\begin{figure}[htp!]  
  \centering
  \scalebox{0.85}{
    \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
      (\parm,\trap) \gets \SimSetup(1^\secpar) \\
      (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
      \adv^{\Oframe}(\parm) \\
      \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\msg,\feval) \in
      \SIG[\uid]: \pcreturn 0 \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
      \pcreturn 0 \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
      \pcreturn 0 \\
      ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},\tyeval^1,\yinsp') \gets
      \ExtractSign(\trap,\Sig) \\
      % \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
      % \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1: \pcreturn 1 \\
      % \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
      % \lor \yinsp \neq \yinsp': \pcreturn 1 \\
      \Yeval=(\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace (\cid_i,
      \attrs_i)\rbrace_i{i\in[n]}, \msg) \\
      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
      \pcreturn 1 \\
      \pcif \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
      \rbrace_{i\in[n]},\msg)
      \neq \yinsp \lor \yinsp \neq \yinsp': \pcreturn 1 \\
      %\textrm{Let~}\scid \gets \lbrace \cid_i \rbrace_{i\in[n]};
      \pcif \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \in \HU: % \land
      %(\cdot,\cdot,\Sig,\Yeval,\msg,\feval) \notin \SIG[\OWNR[\scid]]: \\
      \pcreturn 1 \\
      \pcreturn 0
    }
  }
  \caption{Experiment for non-frameability on \UAS schemes.
    $\Oframe \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\II,\OO,\UU\rbrace
    \CORR,\WREG,\OBTAIN,\SIGN$.}
  \label{fig:exp-uas-frame}
\end{figure}
